\documentclass[11pt,a4paper]{article}

\usepackage[margin=1.5cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[backend=biber,style=numeric]{biblatex}
\addbibresource{mybib.bib}

\titleformat{\section}{\large\bfseries}{}{0pt}{}
\titleformat{\subsection}{\bfseries}{}{0pt}{}

\begin{document}

\begin{center}
{\LARGE \textbf{Olha Makovlieva}}\\[6pt]
.NET Developer\\[6pt]
Dnipro, Ukraine • 068-360-7790 • Olha.Makovlieva@infiz.khpi.edu.ua\\
GitHub: dissomer
\end{center}

\section*{Projects}

\subsection*{Online Cinema Ticket Booking Server (2024–2025)}
\begin{itemize}[noitemsep]
\item Backend server for movie ticket booking with real-time seat availability.
\item REST API for sessions, authentication, showtimes and seat maps.
\item PostgreSQL schema for halls, tickets, schedules.
\item Concurrency handling, validation, secure payment workflow.
\end{itemize}

\subsection*{Language Learning Web Platform (2023–2024)}
Web platform for foreign-language learning with adaptive exercises, vocabulary training, progress tracking and multimedia lessons.

\section*{Most Proud Of}

\begin{itemize}[noitemsep]
\item Strong backend fundamentals in .NET and C\#.
\item Full-cycle problem solving: debugging APIs, Git workflows, databases, Docker.
\item Continuous learning: backend engineering and foreign-language improvement.
\end{itemize}

\section*{Strengths}

C\#, .NET Core, ASP.NET Web API, Entity Framework, SQL, API Design,  
Problem-Solving, Clean Code, Git, Docker Basics

\section*{Languages}

\begin{itemize}[noitemsep]
\item Ukrainian — Native
\item English — Intermediate
\end{itemize}

\section*{Education}

\subsection*{M.Sc. Computer Science (2025–2026)}
National Technical University «KhPI»

\subsection*{B.Sc. Computer Science (2021–2025)}
National Technical University «KhPI»


\section*{Not my publications}

\nocite{*} 
\printbibliography

\end{document}
